%!TEX root = uiuc_2018_invitational.tex
\begin{problem}{Impossible Task}
{stdin}{stdout}
{1 second}{}{}

Spring break is already over. Even though feeling that a one week break is far from enough (as usual), 
you know it is time to resume working. Suddenly, you realize that there is a midterm in Number Theory
coming up next week. As skimming through all the practice questions given by your professor (which 
you should have done over break), you realize that there is one type of question where you have no idea
how to solve. The question is of the form: Given a number $n$, calculate the sum of all divisors of $n$ except
$n$ itself. Even worse, since you never went to any lecture this semester (how surprising), you have no
clue where to begin. However, lucky for you, the professor promised that the given $n$ on the exam would
belong to a certain set of number. Thus, as long as you can memorize all the possible results, you will be
good. Since the size of the given set is rather large, you want to write a program to compute all the answers before
starting memorizing.

\InputFile

The first line contains an integer $q \leq 10^6$ which denotes the number of possible $n$ will be given
on the exam. Each of the next $q$ lines contains an integer $a_i$ which is the $i_{th}$ possible value
($1 \leq a_i \leq 10^6$ $\forall$ $1 \leq i \leq q$).

\OutputFile

The output contains $q$ lines. The $i_{th}$ line should contain an integer which is the answer to the question
with $n = a_i$.

\Examples

\begin{example}
\exmp{
3
1
2
6
}{%
0
1
5
}%
\end{example}

\end{problem}
